Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-10 paper.qmd
Updated PBMC3k reference

This is a benchmark single-cell data set collected on Human Peripheral Blood Mononuclear Cells (PBMC3k) as used in @chen2024. Single-cell data measures the gene expression of individual cells in a sample of tissue (see  for example, @haque2017). This type of data is used to obtain an understanding of cellular level behavior and heterogeneity in their activity. Clustering of single-cell data is used to identify groups of cells with similar expression profiles. NLDR often used to summarise the cluster structure. Usually, NLDR does not use the cluster labels to compute the layout, but uses color to represent the cluster labels when it is plotted. <!-- The purpose of this example is to *illustrate how to use our method to help decide on an appropriate NLDR layout that accurately represents the data*. The cluster results of Human Peripheral Blood Mononuclear Cells (PBMC3k) in @chen2024 are examined.-->

@@

Direct links to videos for viewing online are available in @tbl-links.

```{r}
#| label: tbl-links
#| tbl-cap: "Example videos."
#| tbl-pos: H

links_df <- tibble(
  data = c("PBMC3k"),
  URL = c("link1")
)

links_df |>
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE, 
                    label = "tbllinks") |>
  kableExtra::kable_styling(latex_options = "scale_down")

>>>>

This is a benchmark single-cell data set collected on Human Peripheral Blood Mononuclear Cells (PBMC3k) as used in @pbmc2019. Single-cell data measures the gene expression of individual cells in a sample of tissue (see  for example, @haque2017). This type of data is used to obtain an understanding of cellular level behavior and heterogeneity in their activity. Clustering of single-cell data is used to identify groups of cells with similar expression profiles. NLDR often used to summarise the cluster structure. Usually, NLDR does not use the cluster labels to compute the layout, but uses color to represent the cluster labels when it is plotted. <!-- The purpose of this example is to *illustrate how to use our method to help decide on an appropriate NLDR layout that accurately represents the data*. The cluster results of Human Peripheral Blood Mononuclear Cells (PBMC3k) in @chen2024 are examined.-->

@@
